%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cvExperience
    {Research Associate (Culturally Sensitive Social Robotics for Africa (CSSR4Africa))} % Job title
    {Carnegie Mellon University Africa} % Organization
    {kigali, Rwanda} % Location
    {May 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed smooth gesture execution and socially aware interaction behaviors for the Pepper humanoid robot using ROS/ROS2.}
        \item {Built an LLM-based conversational system with RAG, ASR (Whisper), and TTS for interactive human-robot dialogue.}
        \item {Integrated RTAB-Map SLAM for real-time 3D mapping and autonomous navigation using RGB-D and LiDAR data.}
        \item {Designed custom ROS/ROS 2 drivers to extend and optimize Pepper robot functionality.}
        \item {Upgraded Pepper with NVIDIA Jetson, Intel RealSense, and LiDAR to enhance perception and navigation.}
        \item {Implemented audio-visual perception modules including sound localization (GCC-PHAT), face detection, and mutual gaze estimation.}
      \end{cvitems}
      }
      {\href{www.cssr4africa.org}{Project link}} % Link

%---------------------------------------------------------
\cvExperience
  {Teaching Assistant (Robotics Principle and Practice (Prof David Vernon))} % Job title
  {} % Organization
  {} % Location
  {Sep 2024 - Dec 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Assisted with course grading, including evaluating assignments, tests, and projects related to robot navigation, object manipulation, and vision-based detection.}
      \item {Provided constructive feedback to students on their projects and supported their understanding of robotics concepts through engaging instructional activities.}
      \item {Supported students through one-on-one and group mentoring, troubleshooting software development challenges, and clarifying theoretical concepts.}
    \end{cvitems}
    }
    {\href{http://www.vernon.eu/RPP.htm}{Course link}} % Link

%---------------------------------------------------------
	\cvExperience
	{Teaching Assistant (CMU's flagship deep learning course 11-785 (Prof Bhiksha Raj))} % Job title
	{Carnegie Mellon University Language Technologies Institute(LTI)} % Organization/
	{Pittsburgh, USA (Remote)} % Location
	{May 2023 - Dec 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Guiding over 400 students and mentoring multiple research projects.}
			\item {Covered foundational and advanced topics, including MLPs, CNNs, RNNs, Attention Mechanisms, Transformers, Graph Neural Networks (GNNs), and 
            Hopfield Networks, with practical implementation in PyTorch.}
			\item {Conducted recitations on Hyperparameter Tuning Methods, Normalizations, and optimization techniques for improving model performance}
			\item {Organized and led hackathons and bootcamps for hands-on coding sessions, focusing on key deep learning components like Dataloaders, 
      MLPs, CNNs, and Neural Networks with Attention.}
			\item {Delivered a dedicated recitation on Vision Transformers, including theory, applications, and implementation.}
		\end{cvitems}
	}
  {\href{https://deeplearning.cs.cmu.edu/F23/index.html}{Course link}} % Link

%---------------------------------------------------------
  \cvExperience
    {Research Associate (Amharic OCR (Optical Character Recognition) Project) (Part-time)} % Job title
    {Carnegie Mellon University Africa} % Organization
    {Kigali, Rwanda} % Location
    {June 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing open-source deep learning models for Amharic OCR to improve text recognition accuracy from scanned documents and images.}
        \item {Creating large-scale handwritten and synthetic datasets to augment training data, enhancing model robustness and performance.}
        \item {Utilizing OCR tools and computer vision libraries such as Tesseract and OpenCV to optimize text extraction pipelines.}
        \item {Development of Amharic OCR challenges in collaboration with AI for Good (ITU), supported by a \$10,000 compute grant.}
      \end{cvitems}
    }
    {}


%---------------------------------------------------------
\end{cventries}
