%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvExperience
    {Research Associate (Culturally Sensitive Social Robotics for Africa (CSSR4Africa))} % Job title
    {Carnegie Mellon University Africa} % Organization
    {kigali, Rwanda} % Location
    {May 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted extensive studies on the limitations of the Pepper Humanoid Robot by developing and executing tests for its actuators and sensors.}
        \item {Designed and implemented a custom ROS/ROS2 driver for the Pepper Robot to enhance its functionality.}
        \item {Upgraded the Pepper Robot by integrating advanced hardware, including an NVIDIA Jetson, Intel Real-sense Camera, and YDLIDAR 2 for improved perception and navigation capabilities.}
        \item {Developed advanced sound detection and localization algorithms utilizing GCC-PHAT for precise auditory processing, leveraging inter-aural time differences to enhance directional accuracy.}
        \item {Implemented person detection with YOLOv8 for dynamic path planning in conjunction with RTAB-Map, enhancing the robot's autonomous navigation.}
        \item {Created a robust face detection and mutual gaze detection system to facilitate human-robot interaction through natural and intuitive communication.}
      \end{cvitems}
      }
      {\href{www.cssr4africa.org}{Project link}} % Link

%---------------------------------------------------------
\cvExperience
  {Teaching Assistant (Robotics Principle and Practice (Prof David Vernon))} % Job title
  {} % Organization
  {} % Location
  {Sep 2024 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Assisted with course grading, including evaluating assignments, tests, and projects related to robot navigation, object manipulation, and vision-based detection.}
      \item {Provided constructive feedback to students on their projects and supported their understanding of robotics concepts through engaging instructional activities.}
      \item {Supported students through one-on-one and group mentoring, troubleshooting software development challenges, and clarifying theoretical concepts.}
    \end{cvitems}
    }
    {\href{http://www.vernon.eu/RPP.htm}{Course link}} % Link

%---------------------------------------------------------
	\cvExperience
	{Teaching Assistant (CMU's flagship deep learning course 11-785 (Prof Bhiksha Raj))} % Job title
	{Carnegie Mellon University Language Technologies Institute(LTI)} % Organization/
	{Pittsburgh, USA (Remote)} % Location
	{May 2023 - Dec 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Guiding over 400 students and mentoring multiple research projects.}
			\item {Covered foundational and advanced topics, including MLPs, CNNs, RNNs, Attention Mechanisms, Transformers, Graph Neural Networks (GNNs), and 
            Hopfield Networks, with practical implementation in PyTorch.}
			\item {Conducted recitations on Hyperparameter Tuning Methods, Normalizations, and optimization techniques for improving model performance}
			\item {Organized and led hackathons and bootcamps for hands-on coding sessions, focusing on key deep learning components like Dataloaders, 
      MLPs, CNNs, and Neural Networks with Attention.}
			\item {Delivered a dedicated recitation on Vision Transformers, including theory, applications, and implementation.}
		\end{cvitems}
	}
  {\href{https://deeplearning.cs.cmu.edu/F23/index.html}{Course link}} % Link

%---------------------------------------------------------
\end{cventries}
