%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cvProject
  {Training a Speech Recognizer from Synthetic Data}
  {
    \begin{cvitems}
      \item {Designed a synthetic-data training pipeline for ASR using neural TTS and transformer-based speech models.}
      \item {Generated large-scale synthetic speech–text pairs to replace costly human-annotated datasets.}
      \item {Trained and evaluated ASR models achieving performance comparable to models trained on natural speech.}
    \end{cvitems}
  }
  {Jan 2023 -- May 2023}
  {\href{https://github.com/yohatad/IDL_project}{GitHub}}

%---------------------------------------------------------
\cvProject
  {EEG Foundation Challenge: From Cross-Task to Cross-Subject EEG Decoding}
  {
    \begin{cvitems}
      \item {Built machine learning models for zero-shot transfer across unseen tasks and subjects using EEG data.}
      \item {Developed predictors for mental health–related factors from high-density EEG recordings (128 channels).}
      \item {Worked with large-scale EEG datasets (~700 GB) from 3,000+ participants across multiple experimental paradigms.}
      \item {Benchmarked neural network architectures against demographic and regression-based baselines.}
      \item {Placed 67th among 1,200+ participants worldwide in the EEG Foundation Challenge.}
    \end{cvitems}
  }
  {Sep 2025 -- Dec 2025}
  {\href{https://github.com/yohatad/eeg}{GitHub}}

%---------------------------------------------------------
\end{cventries}
